\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage[utf8]{inputenc}
\usepackage[margin=0.9in,bottom=0in,top=0.4in]{geometry}
%\usepackage{enumitem}


\moderncvtheme[burgundy]{classic}

\name{Julien}{Mourer}
\title{Full Stack Web Developer\vspace*{20pt}}
\AtBeginDocument{\hypersetup{pdftitle = {Julien Mourer - Full Stack Web Developer}}}

\address{9 rue Jocelyn}{69740 Genas, France}
\social[github]{getkey}
\homepage{https://getkey.eu}
\phone[mobile]{+33~651~144~399}
\email{julien.mourer@gmx.fr}
\social[linkedin]{julien-mourer}
\extrainfo{19 years old}


\newcommand{\skillitem}[2]{
	\cvitem[0em]{\textcolor{color1}{#1}}{
		\begin{itemize}%[noitemsep,topsep=0pt]
		\setlength\itemsep{0em}
			#2
		\end{itemize}
	}
}

\newcommand{\projectitem}[3]{
	\cvitem{#1}{\textbf{#2}: #3}
}

\begin{document}

\makecvtitle

\vspace*{-30pt}

\section{Education}
\cventry{2015--2017}{DUT}{Grenoble Alpes University}{Grenoble}{}{Equivalent: Bachelor of Computer Science}
\cventry{2015}{Scientific Baccalauréat}{Lycée Charlie Chaplin}{Lyon}{}{Equivalent: High School Diploma}


\section{Projects}
\projectitem{2016}{\href{http://stereotypemap.info}{Stereotype Map}}{Map that displays national stereotypes fetched from Google Suggestions.}
\projectitem{2016}{\href{http://mywedding.gdn}{MyWedding}}{Website that facilitates wedding organization and communication with guests. Lead developer in a 4-month school project.}
\projectitem{2016}{\href{https://github.com/KordonBleu/enslavism}{Enslavism}}{Framework to help deploying distributed WebRTC peer servers.}
\projectitem{2016}{\href{https://github.com/getkey/rush}{Rush}}{Simple shell with a rudimentary script language.}
\projectitem{2015-2016}{\href{http://jumpsuit.space/}{JumpSuit}}{Multiplayer web game that supports modding, and has a distributed architecture. It is the first game to use WebRTC for client-server communication!}
\projectitem{2015}{\href{https://github.com/KordonBleu/vinage}{Vinage}}{Library to detect collisions. Supports \href{https://en.wikipedia.org/wiki/Wraparound_(video_games)}{wrap-around}. Its cache makes it super fast!}

\section{Languages}
\cvitem{English}{Fluent}
\cvitem{French}{Native speaker}
\cvitem{German}{Basic conversational abilities}

\section{Skills}
\skillitem{Web development}{
\item JavaScript (ES5 \& ES6), Vue.js, Vuex
	\item PostgreSQL, MongoDB
	\item HTML, CSS, Stylus
	\item Node.js, PHP, Nginx, Apache
	\item Express, Koa
	\item Rollup, Babel
}
\skillitem{Software development}{
	\item UML, design patterns
	\item C/C++, Java, Python, Rust
}
\skillitem{Online multiplayer game development}{
	\item Authoritative server, prediction
	\item Custom protocols, Protobuf
	\item Websockets, WebRTC, UDP
}

\section{Interests}
\cvitem{Skiing}{Grenoble is surrounded by mountains - winter is awesome!}
\cvitem{Design}{I took a 6-month design course to be able to do freelance work. I fell in love with the discipline.}
\cvitem{Chiptune}{I love this genre. Sometimes I try to compose.}

\end{document}
